\documentclass[]{article}

% Imported Packages
%------------------------------------------------------------------------------
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
%\usepackage{extarrows}
\usepackage{setspace}
%------------------------------------------------------------------------------

% Header and Footer
%------------------------------------------------------------------------------
\pagestyle{plain}  
\renewcommand\headrulewidth{0.4pt}                                      
\renewcommand\footrulewidth{0.4pt}                                    
%------------------------------------------------------------------------------
\title{Software Requirements Specifications}
\author{Team 1}                               
%------------------------------------------------------------------------------

\newcommand{\sname}{Movie Matcher}

% Document

\begin{document}

\maketitle	

\section{Non-Functional Requirements} \label{nfreq}
\label{sec:non-functional_requirements}
% Begin Section
\subsection{Look and Feel Requirements}
\label{sub:look_and_feel_requirements}
% Begin SubSection


\subsubsection{Appearance Requirements}
\label{ssub:appearance_requirements}
\newcounter{placeholder}
% Begin SubSubSection
\begin{enumerate}[{LF}1. ]
	\item The application should be visually appealing to anyone using it.
	\item The interface should be descriptive, telling the user what to do and how to do it.
	\item The query search and the experts should be easily visible.
	\item The results displayed should be easily readable.
	\setcounter{placeholder}{\theenumi}
\end{enumerate}
% End SubSubSection

\subsubsection{Style Requirements}
\label{ssub:style_requirements}
\begin{enumerate}[{LF}5. ]
	\item The overall design should look familiar to other query based applications.
% Begin SubSubSection
\end{enumerate}


\subsection{Usability and Humanity Requirements}
\label{sub:usability_and_humanity_requirements}
% Begin SubSection

\subsubsection{Ease of Use Requirements}
\label{ssub:ease_of_use_requirements}
% Begin SubSubSection
\begin{enumerate}[{UH}1. ]
	\item The application should be easy to use (easy to navigate, surf, search, get results, etc.) just like an ideal query processing software like google, wikipedia, etc.
	\item The overall functionality of the application should be basic, a child of 10 years or older should be able to use it.
	\item The application should be designed in a way that query-processing is not difficult.
% End SubSubSection

\subsubsection{Personalization and Internationalization Requirements}
\label{ssub:personalization_and_internationalization_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}
% End SubSubSection

\subsubsection{Learning Requirements}
\label{ssub:learning_requirements}
	\item People who are new to query processing software should be able to learn how to use it within 10-20 minutes of full time usage.
% Begin SubSubSection
	

\subsubsection{Understandability and Politeness Requirements}
\label{ssub:understandability_and_politeness_requirements}
	\item The product shall use symbols and words that are naturally understandable by the user community.

\subsubsection{Accessibility Requirements}
\label{ssub:accessibility_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}
\end{enumerate}

% End SubSection

\subsection{Performance Requirements}
\label{sub:performance_requirements}
% Begin SubSection

\subsubsection{Speed and Latency Requirements}
\label{ssub:speed_and_latency_requirements}
% Begin SubSubSection
\begin{enumerate}[{PR}1. ]
	\item The application should be able to present the results of a search requested by the user within five seconds of the request being made.
	\item The application should be respond within three seconds to a user command other than a search (open, close, etc.).
% End SubSubSection

\subsubsection{Safety-Critical Requirements}
\label{ssub:safety_critical_requirements}
% Begin SubSubSection
	\item The application should project proper lighting on the screen (prevent seizures and blindness).
% End SubSubSection

\subsubsection{Precision or Accuracy Requirements}
\label{ssub:precision_or_accuracy_requirements}
	\item The software shall provide at most 10 different movies when a query search is made.
	\item The software shall perform the exact search the user requests. It shall not assume a different spelling (i.e. to correct a spelling mistake, etc.).


\subsubsection{Reliability and Availability Requirements}
\label{ssub:reliability_and_availability_requirements}
	\item The product should be usable for 24 hours per day, 365 days per year.
% End SubSubSection

\subsubsection{Robustness or Fault-Tolerance Requirements}
\label{ssub:robustness_or_fault_tolerance_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}

\subsubsection{Capacity Requirements}
\label{ssub:capacity_requirements}
	\item The application shall allow at most one user to operate the software.
	\item The application shall permit the user to make a query for only one particular movie at a time.
% End SubSubSection

\subsubsection{Scalability or Extensibility Requirements}
\label{ssub:scalability_or_extensibility_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}

% End SubSubSection

\subsubsection{Longevity Requirements}
\label{ssub:longevity_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Operational and Environmental Requirements}
\label{sub:operational_and_environmental_requirements}
% Begin SubSection

\subsubsection{Expected Physical Environment}
\label{ssub:expected_physical_environment}
% Begin SubSubSection
\begin{enumerate}[{OE}1. ]
	\item The product shall run on any android platform device along with computers, tablets, PC’s, and cellphones (other devices that support Android).
	\item The product will be user friendly as it will allow them to use the application indoors and outdoors provided they have a 
wifi connection.
% End SubSubSection

\subsubsection{Requirements for Interfacing with Adjacent Systems}
\label{ssub:requirements_for_interfacing_with_adjacent_systems}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}

\subsubsection{Productization Requirements}
\label{ssub:productization_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}

\subsubsection{Release Requirements}
\label{ssub:release_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}
\end{enumerate}


\subsection{Maintainability and Support Requirements}
\label{sub:maintainability_and_support_requirements}
% Begin SubSection

\subsubsection{Maintenance Requirements}
\label{ssub:maintenance_requirements}
% Begin SubSubSection
\begin{enumerate}[{MS}1. ]
	\item The software should easily be modifiable just in case the user decides to add more functionality to the application.

\subsubsection{Supportability Requirements}
\label{ssub:supportability_requirements}
% Begin SubSubSection
	\item The application should be able to be used in various platforms such as Windows, Macintosh, and Android.
	\item The application will have a help section within the software to allow the user to search for a solution to their problems (connectivity, query processing, etc.).
% End SubSubSection

\subsubsection{Adaptability Requirements}
\label{ssub:adaptability_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}
\end{enumerate}

% End SubSection

\subsection{Security Requirements}
\label{sub:security_requirements}
% Begin SubSection

\subsubsection{Access Requirements}
\label{ssub:access_requirements}
% Begin SubSubSection
\begin{enumerate}[{SR}1. ]
% End SubSubSection

\subsubsection{Integrity Requirements}
\label{ssub:integrity_requirements}
	\item The application shall use encryption to protect transactions being sent from the user to the client.
	\item The application shall make sure queries are made with proper spell check (provide the user with a "did you mean" suggestion, etc.).
	\item The application shall protect itself from viruses and other malware attacks (prompting the computer to virus scan, etc.).
% End SubSubSection

\subsubsection{Privacy Requirements}
\label{ssub:privacy_requirements}
% Begin SubSubSection
	\item The application should protect the identity of the person using the software. It shall not pass personal information (if any) to any unknown party without the explicit permission of the user.
% End SubSubSection

\subsubsection{Audit Requirements}
\label{ssub:audit_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}
% Begin SubSubSection


\subsubsection{Immunity Requirements}
\label{ssub:immunity_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Cultural and Political Requirements}
\label{sub:cultural_and_political_requirements}
% Begin SubSection

\subsubsection{Cultural Requirements}
\label{ssub:cultural_requirements}
% Begin SubSubSection
\begin{enumerate}[{CP}1. ]
	\item The application should not use symbols, text, or media which debases a race, culture, or a political landscape.
% End SubSubSection

\subsubsection{Political Requirements}
\label{ssub:political_requirements}
	\item The application shall use experts primarily based on North America (Canada or the United States). 
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Legal Requirements}
\label{sub:legal_requirements}
% Begin SubSection

\subsubsection{Compliance Requirements}
\label{ssub:compliance_requirements}
% Begin SubSubSection
\begin{enumerate}[{LR}1. ]
	\item The application should abide by any privacy and copyright laws.
	\item The use of experts shall be done, whilst the owner permits its free usage.
% End SubSubSection

\subsubsection{Standards Requirements}
\label{ssub:standards_requirements}
\begin{enumerate}[{N/A} ]
	\item
\end{enumerate}
\end{enumerate}


% End Section
\end{document}